\chapter*{ABSTRACT}
\begin{center}
  \large
  \textbf{    \emph{POSE BASED} SEMAPHORE PREDICTION USING DEEP LEARNING }
\end{center}
% Menyembunyikan nomor halaman
\thispagestyle{empty}

\begin{flushleft}
  \setlength{\tabcolsep}{0pt}
  \bfseries
  \begin{tabular}{lc@{\hspace{6pt}}l}
  Student Name / NRP&: &Muhammmad Daffa ZW / 07211940000064\\
  Department&: &Computer Engineering FTEIC - ITS\\
  Advisor&: &1. Dr. Eko Mulyanto Yuniarno, S.T., M.T.\\
  & & 2.  Ahmad Zaini, S.T., M.T.\\
  \end{tabular}
  \vspace{4ex}
\end{flushleft}
\textbf{Abstract}

% Isi Abstrak
The visual communication system using semaphore has been widely used in various fields such as the military, maritime, and transportation sectors. This method involves the use of flags or hand signals to transmit messages between two or more parties. However, traditional semaphore usage requires special training, expertise, and the ability to understand complex semaphore codes.This research aims to develop a semaphore pose recognition system using MediaPipe and Deep Learning classification through Convolutional Neural Network (CNN) methods. The development process involves steps such as dataset collection and processing, pose extraction using MediaPipe, and pose classification using CNN models such as CNN, CNN ResNet50V2, and CNN Xception.The results of this research demonstrate that the developed system is capable of accurately detecting letters and words in semaphore poses. The CNN ResNet50V2 model achieved an accuracy of 98.08\%, CNN Xception achieved 98.78\%, CNN achieved 98.94\%, and CNN2 achieved 99.1\%. Based on these findings, the semaphore pose recognition system has potential applications in education, particularly in schools. With the help of this technology, learning about semaphore can become more engaging and interactive. Students can learn visual communication through semaphore with the assistance of a system that can detect and recognize letter and word poses. The use of the semaphore pose recognition system in education also opens up possibilities for further exploration in the development of other interactive learning methods.


\vspace{2ex}
\noindent
\textbf{Keywords: \emph{Semaphore, MediaPipe, Convolutional Neural Network , Human Pose, Deep Learning , Xception , ResNet50V2 }}